%-------------------------
% Resume in Latex
% Author : Daniel Palma
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape First Last} \\ \vspace{1pt}
    \href{mailto:first.last@ucf.edu}{\underline{first.last@ucf.edu}} $|$ \href{mailto:first@last.dev}{\underline{first@last.dev}} $|$ 
    \href{https://linkedin.com/in/firstlast}{\underline{linkedin.com/in/firstlast}} $|$
    \href{https://github.com/firstlast}{\underline{github.com/firstlast}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University}{City, State}
      {B.S. in Computer Science, Minor in Mathematics 3.9/4.0 GPA}{Expected Graduation: 2026}
    
      \vspace{-15pt}
    \resumeSubheading
      {}{}
      {\scriptsize{\textbf{Relevant Coursework: }Data Structures and Algorithms, Object Oriented Programming, Discrete Mathematical Structures, Computer Logic}}{}
  \resumeSubHeadingListEnd


  %-----------EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart
    
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubheading
  {Undergraduate Teaching Assistant}{August 2023 - December 2023}
  {University}{City, State}
  \resumeItemListStart
    \resumeItem{Lead teaching assistant for the introductory data structures course}
    \resumeItem{Coordinated lab lectures for over 5 sections and assignments for over 100 students and 5 lab sections}
    \resumeItem{Engaging with students through weekly office hours for assignment assistance.}

  \resumeItemListEnd

  \resumeSubheading
    {Peer Tutor}{August 2021 - May 2022}
    {Highschool}{City, State}
    \resumeItemListStart
      \resumeItem{Aided students in C and Java programming develop a solid understanding of the language.}
      \resumeItem{Provided students with resources in order to properly identify and solve problems, resulting in an average of 15\% greater test scores}
      \resumeItem{Collaborated with other Peer Tutors to hold weekly group review sessions of 30+ students.}
      \resumeItem{Demonstrated how to implement complex data structures and algorithms into programs resulting in a 45\% greater passing rate on assignments.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart


  \resumeProjectHeading
  {\textbf{Project 1} $|$ \emph{React, Next.js, TypeScript, Tailwind CSS, Azure AI Vision, PostgreSQL, Supabase, Plaid API, GPT3.5}}{}
  \resumeItemListStart
    \resumeItem{Awarded 2nd Place in Google's Empowering Learners with Technology challenge at ShellHacks 2023.}
    \resumeItem{Led development in implementing the database, user authentication, and API.}
    \resumeItem{Implemented user authentication using Supabase Auth and OAuth2 social providers}
    \resumeItem{Utilized Azure’s AI Vision and OpenAI’s ChatGPT API to seamlessly extract and correlate receipt data with bank transactions.}
    \resumeItem{Leveraged GPT3.5 and Supabase Buckets to cache responses and reduce API calls.}
    \resumeItemListEnd
    
  \resumeProjectHeading
      {\textbf{Project 2} $|$ \emph{React, Next.js, Typescript, Tailwind CSS, PostgreSQL, Supabase}}{}
      \resumeItemListStart
        \resumeItem{Developed a full stack interactive dashboard using Next.js and Supabase. }
        \resumeItem{Modeled PostgreSQL database schemas and policies for data using row level security.}
        \resumeItem{Handled user authentication and sign up with oAuth providers through Supabase Auth}
        \resumeItem{Communicates with the PostgreSQL database using a RESTful API.}
      \resumeItemListEnd

        \resumeProjectHeading
      {\textbf{Project 3} $|$ \emph{Python, Discord.py, BeautifulSoup}}{}
      \resumeItemListStart
        \resumeItem{Utilizes the Requests and BeautifulSoup libraries to monitor online retailers to extract item titles and prices.}
        \resumeItem{Leverages the discord.py library to connect to Discord's API and send alerts to users through designated channels.}
        \resumeItem{Enables users to monitor prices in real-time and sends alerts when they meet desired thresholds.}
      \resumeItemListEnd


  \resumeProjectHeading
      {\textbf{Project 4} $|$ \emph{TypeScript, Tailwind CSS, Next.js}}{}
      \resumeItemListStart
        \resumeItem{Created a Next.js single-page Pomodoro timer application for improved productivity and focus.}
        \resumeItem{Leveraged Next.js to optimize performance and deliver a responsive website, improving loading times and navigation.}
        \resumeItem{implemented TypeScript for type safety and code quality, ensuring robustness and minimizing errors}
      \resumeItemListEnd

\resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, C++, SQL (Postgres), JavaScript, TypeScript, HTML, CSS} \\
     \textbf{Frameworks}{: React, Node.js, Next.js, Tailwind CSS} \\
     \textbf{Tools}{: Git, Github, Docker, Vercel, Linux, Heroku, LaTeX, Supabase} \\
    }}
 \end{itemize}


%-----------------------------------------


%-------------------------------------------

\section{Organizations}

\resumeSubHeadingListStart
\resumeProjectHeading
          {\textbf{Knight Hacks} $|$ \emph{Member}}{}
          \resumeItemListStart
            \resumeItem{Hack-A-Day 2 Winner: Project 5}
          \resumeItemListEnd
\resumeSubHeadingListEnd

%
\end{document}