

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Daniel Palma}} & Email: \href{mailto:}{dany@dpalma.dev}\\
    \textit{Software Engineer} &
  \href{https://github.com/danypalma}{Github: ~~github.com/danypalma} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Central Florida}{Orlando, Florida}
      {Bachelor of Science in Computer Science, Minor in Mathematics. 3.8/4.0 GPA}{Expected Graduation: 2026}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Relevant Coursework:} Computer Science 1, Discrete Mathematical Structures, Object Oriented Programming, Statistical Methods}}}
    \resumeSubHeadingListEnd
	    
\vspace{-10pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~C, Java, Python, JavaScript, TypeScript, HTML/CSS, LaTeX}
	\resumeSubItem{Frameworks}{~~~~React, Next.js, Node.js, Tailwind CSS, Discord.py}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, Github, Docker, Vercel, Netlify}
	\resumeSubItem{Platforms}{~~~~~~~Linux, MacOS, Windows }
    \resumeSubItem{Languages}{~~~~~~~Spanish, English}

\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading{Developer}{Aug 2022 - Present}
{Knight Hacks}{ Orlando, FL}
\resumeItemListStart
    \resumeItem{}
    {Aided in development of yearly Hackathon website and Admin Tool using Next.js}
    \resumeItem{}
    {Integrated Tailwind CSS to create an aesthetically pleasing User Interface.}
    \resumeItemListEnd
  
\vspace{-3pt}

\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading{Peer Tutor}{Aug 2021 - May 2022}
{Cypress Bay High School}{Weston, FL}
\resumeItemListStart
    \resumeItem{}
    {Aided students in C and Java programming develop a solid understanding of the language.}
    \resumeItem{}
    {Collaborated with other Peer Tutors to hold weekly review sessions.}     
    \resumeItem{}
    {Provided students with resources in order to properly identify and solve problems.}
    \resumeItem{}
    {Demonstrated how to implement complex data structures and algorithms into functional programs.}
  \resumeItemListEnd
  
\vspace{-3pt}

\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Projects}

\resumeSubHeadingListStart

\resumeSubheading{Personal Portfolio}{}
{Javascript, React, CSS Modules}{}
\resumeItemListStart
    \resumeItem{}
    {Developed a personal portfolio using the React framework.}
    \resumeItem{}
    {Exercised the use of CSS Modules to create reusable conflict free CSS.}     
    \resumeItem{}
    {Hosting the site on Netlify and managing traffic on Google domains.}  
  \resumeItemListEnd
  
\vspace{-3pt}

\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading{DealDetector}{}
{Python, Discord.py, BeautifulSoup }{}
\resumeItemListStart
    \resumeItem{}
    {Utilizes the Requests and BeautifulSoup libraries to monitor online retailers to extract item titles and prices.}        
    \resumeItem{}
        {Leverages the discord.py library to connect to Discord's API and send alerts to users through designated channels.}
      \resumeItem{}
      {Enables users to monitor prices in real-time and sends alerts when they meet desired thresholds.}
  \resumeItemListEnd
  
\vspace{-3pt}

\resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading{Pomo.io}{}
    {Typescript, TailwindCSS, Next.js} {}
    \resumeItemListStart
        \resumeItem{}
          {Created a Next.js single-page Pomodoro timer application for improved productivity and focus.}
        \resumeItem{}
            {Leveraged Next.js to optimize performance and deliver a responsive website, improving loading times and navigation.}
          \resumeItem{}
          {Styled UI components using Tailwind CSS, allowing for consistency and utility-first fundamentals.}
          \resumeItem{}
          {Implemented TypeScript for type safety and code quality, ensuring robustness and minimizing errors.}
      \resumeItemListEnd
      
\vspace{-3pt}

\resumeSubHeadingListEnd


%-----------ORGANIZATIONS -----------------
\vspace{-5pt}
\section{Organizations}

\resumeSubHeadingListStart
\resumeSubheading{Knight Hacks}{}
{}{}
\vspace{-20pt}
\begin{itemize}
  \item Hack-A-Day 2 Winner: KnightsWallet
\end{itemize}
\resumeSubHeadingListEnd

\vspace{-15pt}

\resumeSubHeadingListStart
\resumeSubheading{Society of Hispanic Professional Engineers}{}
{Member}{}

\resumeSubHeadingListEnd

\vspace{-15pt}

\resumeSubHeadingListStart
\resumeSubheading{Google Student Developer Club}{}
{Member}{}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {National Additive Manufacturing Competition Finalist @ SkillsUSA NLSC - July 2022}
\vspace{-5pt}
\item {Top Engineering Student @ Cypress Bay High School - June 2022 }
\vspace{-5pt}
\item {AP Scholar with Distinction - May, 2021}

\end{description}

\vspace{-5pt}


\end{document}